\documentclass[12pt]{amsart}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\setlength{\textheight}{8.5in} \setlength{\textwidth}{6.4in}
\setlength{\hoffset}{-0.75in}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amscd,xcolor}
\usepackage{amsmath,multirow,tabularx}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{enumerate,graphicx,leftidx}
\usepackage{amsmath,amsthm,hyperref} %加了 hyperref 后, 用 PDFLaTeX 编译得到的文件有超链接, 方便屏幕阅读
%\usepackage[notref,notcite]{showkeys} %定稿后此行去掉

\usepackage{fancyhdr}
%%%%%设置页眉
\pagestyle{fancy} \lhead{}
 \chead[Shen]{X-ray CT reconstruction via wavelet frame and nonlocal Low-Rank regularization}
  \rhead{}
  %%0pt表示删除页眉下划线
\renewcommand{\headrulewidth}{0pt}
%%%%%设置页眉


\numberwithin{equation}{section}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{comparison}[theorem]{Comparison}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{note}[theorem]{Note}
\newenvironment{proof1}[1]
[Proof]{\begin{trivlist}\item[\hskip\labelsep{\itshape Proof of
theorem #1.}]}{\end{trivlist}}
%%%%%%%%%%%%%%%%%%%%%符号简写%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\R}{{\mathbb R}}
\newcommand{\eps}{\epsilon}
\begin{document}
\title{X-ray CT reconstruction via wavelet frame and nonlocal Low-Rank regularization}

 %    Remove any unused author tags.

 %    author one information
 \author{Yanfeng Shen}
 \address{College of Mathematical Science, Dezhou University, Dezhou, Shandong253023, China}
 %\curraddr{}
 \email{shyf8584@163.com}
 \thanks{
This work was supported by
Science and Technology Research Program for Universities in Shandong Province, China(grant NO. J16LI58). }

 %    author two information
 %\thanks{}


 \subjclass[2000]{42C15, 94A12}

 \keywords{Radon transform; Image inpainting; Nonlocal Low-Rank regularity}

 %\date{}

 %\dedicatory{}
 \maketitle
\begin{abstract}
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%第一节__介绍%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Medical imaging application of X-ray computed tomography(CT) include cranial,chest, cardiac
abdominal and pelvic imaging. The so widely used of CT due to the ability of viewing interior
structures without destroying the surface of organs or subjects. However, the radiation caused
by X-ray during imaging do harm to patients' health. Thus, the approximately lossless image
reconstruction based on low dose X-Ray, like reducing the number of projections, is {\color{red!70}
continuously} concerned by scientists and doctors. The basic model of X-ray reconstruction problem
can be represented as a linear inverse problem,
%------------------公式1.1-------------------------%
\begin{equation}\label{basic_1}
Pu=f
\end{equation}
%------------------公式1.1-------------------------%
where $P\in \R^{m\times n}$ is a projection operator represents the collection of discrete
line integrations at different projection angles and along different beamlets. Numerically
$P$ is realized by Siddon's algorithm.{\color{blue!70} [Dongbin11,[2]]}

When small number of projections are used, i.e. $m<n$, the matrix $P$ is rank deficiency. A a
result, \eqref{basic_1} will have infinity many solutions, there are many methods for deriving
a useful result from them. {\color{blue!70} [add several reference]} The solutions
by filtered back projection (FBP) algorithm{\color{blue!70} [Dongbin11,[10]]} and algebraic
reconstruction technique (ART) {\color{blue!70} [Dongbin11,[13]]}, are usually contains artifacts and
thus unreliable reconstructed.

In practice, the projection image $f$ usually contains noise. Gaussian noise {\color{blue!70} [add several reference]} and Poisson noise ({\color{blue!70} [Donbin11,36,16]}) both are considered to
simulate the realistic environment. Thus, the basic model \eqref{basic_1} is modified by
%------------------公式1.2-------------------------%
\begin{equation}\label{basic_2}
f=Pu+\eps
\end{equation}
%------------------公式1.2-------------------------%
To suppress noise, and artifacts(unregularities locally) while reconstruction of
image, usually tiny structures should be contained in, fidelity and {\color{green!80} noun idea},
various differential operator based regularization methods,
like variational approach (total variation(TV),{\color{red!70} [14],[1-3]}) and wavelet frame based method ({\color{red!70} [6],[22]}), have been proposed and received acceptability results both
in vision and computational error. one of the standard forms for TV-based image reconstruction
model can be written as
%------------------公式1.3-------------------------%
\begin{equation}\label{TVmodel}
\min_u \frac{1}{2}\|Pu-f\|_2^2+\lambda \|\nabla u\|_1.
\end{equation}
%------------------公式1.3-------------------------%
What needed to mention is that, the authors of {\color{red!70}[ ] } establised a rigorous  connection
between one of the wavelet frame based approach, called the analysis based approach, and variational
models. The authors proposed a new model used the analysis based approach of wavelet frame method, and built in a Radon domain inpainting, which can improve the {\color{blue! 70}resolution}.
 %------------------公式1.3-------------------------%
\begin{align}\label{Wmodel_1}
\min_{f,u} \frac{1}{2}\|R_{(\omega\backslash\Lambda)}(Pu-f)\|_2^2&+\lambda_1 \|W_1 f\|_{1,2}+\lambda_2 \|W_2 u\|_{1,2}+\\
&\frac{K}{2}\|R_\Lambda f-f_0\|_2^2+\frac{1}{2}\|R_\Lambda (Pu)-f_0\|_2^2,\nonumber
\end{align}
%------------------公式1.3-------------------------%
where the norm $\|\cdot\|_{1,2}$ is isotropic $l_1$ norm defined as,
$$$$  

\end{document}
